---
title: "Homework 3"
output:
  pdf_document: default
  html_document: default
---

```{r, message = FALSE, warning = FALSE}
library(faraway)
library(readr)
md23 <- read.csv(here::here("Data", "minmax_dec2023.csv"))
nba_total <- read.csv(here::here("Data", "nbatotal_2022_23.csv"))
```

# Question 1B
```{r}
mod <- lm(TMAX ~ TMIN, data=md23)
sumary(mod)
```

# Question 1C
There does appear to be evidence of a significant relationship, as the p-value is significant at the 0.05 level. 

# Question 1D
45.52559
32.50739 + 0.43394(30) = 45.52559

# Question 1E
The errors may not be independent since there are usually many hot days or many cold days together. 

# Question 1F
```{r}
residuals <- resid(mod)
plot(md23$TMIN, residuals)
abline(h=0)
```
I don’t think there are any violations. There looks to be little more variance towards the middle of the graph, but I don’t think you could conclude there is non-constant variance overall. 

# Question 2A
```{r}
nba_total2 <-nba_total[nba_total$MP >= 96,]
nrow(nba_total) - nrow(nba_total2)
```
70 players. 

# Question 2B
```{r}
plot(nba_total2$AST, nba_total2$TOV)
```
The relationship looks fairly linear, so you could use simple linear regression. 

# Question 2C
```{r}
mod <- lm(TOV ~ AST, data=nba_total2)
sumary(mod)
```
75% of the variance in the response is explained by total assists. 

# Question 2D
```{r}
mod1 <- lm(TOV ~ AST + MP + FGA, data=nba_total2)
sumary(mod1)
```
88% of the variance in the response is explained by our model. 

# Question 2E
Minutes played doesn’t seem like a useful predictor because the p-value is 0.89, which doesn’t suggest significance. 

# Question 2F
```{r}
mod2 <- lm(TOV ~ AST + FGA, data=nba_total2)
summary(mod2)
```
19.82 is our estimate of the standard deviation of the regression errors. 

# Question 3A
```{r}
data(cheddar)
mod <- lm (taste ~ Acetic + H2S + Lactic, data=cheddar)
summary(mod)
```
BetaAcetic = 0.32774
BetaH2S = 3.91184
BetaLactic = 19.67054

# Question 3B
```{r}
r2 <- cor(fitted(mod), cheddar$taste)**2
r2
```
This is the R-Squared in the regression output. 












