---
title: "Homework 1"
output:
  pdf_document: default
  html_document: default
---

```{r, message = FALSE, warning = FALSE}
library(faraway)
library(readr)
ph <- read.csv(here::here("Data", "president_heights.csv"))
```

# Question 1A
```{r}
seq(1, 10, 3)
```
This is a vector that lists numbers from 1 to 10 inclusive, going up by three each time. 

# Question 1B
```{r}
seq(1, 100, 2)
```

# Question 1C
```{r}
vec <- c(36, 23, 20, 29)
vec - 5
```
The smallest number is 15. Error: unexpected ',' in "vec <- (36,"

# Question 1D
```{r}
sizes <- c("small", "medium", "large")
popcorn <- sample(sizes, 25, replace=TRUE, prob=c(0.2, 0.5, 0.3))
popcorn_counts <- table(popcorn)
popcorn_counts
```
I ordered 8 large popcorns. The sample function will sample from the ‘sizes’ vector 25 times with accompanying probabilities: small=0.2, medium=0.5, large=0.3. This sampling is random, so you will get different values each time. 

# Question 1E
```{r}
barplot(popcorn_counts, main='Frequency of Popcorn Size', 
        xlab='popcorn size', ylab='frequency')
```

# Question 2A
```{r}
colnames(ph) <- c("President", "Height_in")
head(ph)
```

# Question 2B
```{r}
hist(ph$Height_in, main="President Height", xlab="Height(in)", ylab="Frequency")
```

# Question 2C
```{r}
summary(ph$Height_in)
```

# Question 3
```{r}
data(cheddar)
dim(cheddar)
```

