---
title: "Homework7"
output:
  pdf_document: default
  html_document: default
---

```{r, message = FALSE, warning = FALSE}
library(faraway)
library(readr)
library(leaps)
eagle_data <- read.csv(here::here("Data", "lead_eagles_iowa.csv"))
```


# Question 1
```{r}
data(prostate)
head(prostate)
lm_prostate <- lm(lpsa ~ ., data=prostate)
summary(lm_prostate)
```

# Question 1A
```{r}
# Backward Elimination
drop1(lm_prostate, test='F')
lm_prostate1 <- update(lm_prostate, . ~ . - gleason)
drop1(lm_prostate1, test='F')
lm_prostate2 <- update(lm_prostate1, . ~ . - lcp)
drop1(lm_prostate2, test='F')
lm_prostate3 <- update(lm_prostate2, . ~ . - pgg45)
drop1(lm_prostate3, test='F')
lm_prostate4 <- update(lm_prostate3, . ~ . - age)
drop1(lm_prostate4, test='F')
lm_prostate5 <- update(lm_prostate4, . ~ . - lbph)
drop1(lm_prostate5, test='F')
```
Best Model: lpsa ~ lcavol + lweight + svi

# Question 1B
```{r}
# AIC
prostate_null <- lm(lpsa ~ 1, data=prostate)
prostate_scope <- reformulate(colnames(prostate)[1:8])
prostate_aic <- step(prostate_null, scope=prostate_scope, direction='forward', trace=0)
summary(prostate_aic)
```
Best Model: lpsa ~ lcavol + lweight + svi + lbph + age

# Question 1C
```{r}
# Adjusted R^2
prostate_subsets <- regsubsets(lpsa ~ ., data=data.frame(prostate))
rs <- summary(prostate_subsets)
data.frame(rs$outmat, rs$adjr2)
```
The model with the highest adjusted r^2 is 
lpsa ~ lcavol + lweight + age + lbph + svi + lcp + pgg45 at 0.627. However, the much simpler model lpsa ~ lcavol + lweight + svi has a very similar r^2 of 0.614. 

# Question 1D
```{r}
# Mallow's Cp
plot(1:8, rs$cp, ylim = c(0,26), xlim = c(1,8))
abline(0,1)
```
The model with the lowest Mallows CP is lpsa ~ lcavol + lweight + lbph + svi. I would say this is also fairly close to the Cp = p line, and the marginal benefit of adding more predictors is quite low. 


# Question 2
```{r}
data(teengamb)
head(teengamb)
lm_gamble <- lm(gamble ~ ., data=teengamb)
summary(lm_gamble)
```

# Question 2A
```{r}
# Backward Elimination
drop1(lm_gamble, test='F')
lm_gamble1 <- update(lm_gamble, . ~ . - status)
drop1(lm_gamble1, test='F')
lm_gamble2 <- update(lm_gamble1, . ~ . - verbal)
drop1(lm_gamble2, test='F')
```
Best Model: gamble ~ sex + income

# Question 2B
```{r}
# AIC
gamble_null <- lm(gamble ~ 1, data=teengamb)
gamble_scope <- reformulate(colnames(teengamb)[1:4])
gamble_aic <- step(gamble_null, scope=gamble_scope, direction='forward', trace=0)
summary(gamble_aic)
```
Best Model: gamble ~ income + sex + verbal

# Question 2C
```{r}
# Adjusted R^2
gamble_subsets <- regsubsets(gamble ~ ., data=data.frame(teengamb))
rs_gamble <- summary(gamble_subsets)
data.frame(rs_gamble$outmat, rs_gamble$adjr2)
```
The model with the highest adjusted r^2 is gamble ~ sex + income + verbal at 0.493; however, gamble ~ sex + income has a comparable adjusted r^2 of 0.479. 

# Question 2D
```{r}
# Mallows Cp
plot(1:4, rs_gamble$cp, ylim=c(0,12))
abline(0,1)
```
The model with the minimum Mallows CP, which is also on the Cp=p line is gamble ~ sex + income + verbal. 

# Question 3
```{r}
data(trees)
head(trees)
lm_trees <- lm(log(Volume) ~ Height * Girth, data=trees)
summary(lm_trees)
```
It would not make sense to simplify this model because both of the predictors and the interaction term are highly significant. 

# Question 4A
```{r}
data(gala)
head(gala)
lm_gala <- lm(Species ~ Area + Elevation + Nearest + Scruz + Adjacent, data=gala)
summary(lm_gala)
```

# Question 4B
```{r}
data(galamiss)
head(galamiss)
lm_galamiss <- lm(Species ~ Area + Elevation + Nearest + Scruz + Adjacent, data=galamiss)
summary(lm_galamiss)
```

# Question 4C
```{r}
lm_elevation <- lm(Elevation ~ Area + Nearest + Scruz + Adjacent, data=galamiss)
summary(lm_elevation)

pred_vals <- predict(lm_elevation, galamiss[is.na(galamiss$Elevation), ])

galamiss_imputed <- data.frame(galamiss)
galamiss_imputed$Elevation[is.na(galamiss$Elevation)] <- pred_vals

lm_galamiss2 <- lm(Species ~ Area + Elevation + Nearest + Scruz + Adjacent, data=galamiss_imputed)
summary(lm_galamiss2)
```
The R-squared decreases a little in our imputed model, and Adjacent becomes a more significant predictor. 

# Question 5A
```{r}
head(eagle_data)
xtabs( ~ Lead_level_code + Released, data=eagle_data)
```

# Question 5B
```{r}
# Conditional Probability: Released on Background
54/(54+80)

# Conditional Probability: Released on Sub-Clinical
10/(27+10)

# Conditional Probability: Released on Clinical
5/(94+5)
```

# Question 5C
```{r}
# Logistic Regression
eagle_glm <- glm((Released=="R")*1 ~ Lead_level_code, data=eagle_data, family = 'binomial')
summary(eagle_glm)

# Background 
exp(-0.3930)/(1+exp(-0.3930))

# Sub-Clinical
exp(-0.3930 - 0.6002)/(1+exp(-0.3930 - 0.6002))

# Clinical
exp(-0.3930 - 2.5408)/(1+exp(-0.3930 - 2.5408))
```
These probabilities are the same as those calculated in part b. 

