---
title: "Homework 2"
output:
  pdf_document: default
  html_document: default
---

```{r, message = FALSE, warning = FALSE}
library(faraway)
library(readr)
le_gdp <- read.csv(here::here("Data", "lifeexp_gdp.csv"))
```

# Question 1A
```{r}
head(le_gdp)
```

# Question 1B
```{r}
nrow(le_gdp)
```

# Question 1C
Because it’s likely the wealth, and thus the resources of the country, will contribute to better healthcare, which could cause people to live longer. 

# Question 1D
```{r}
plot(le_gdp$gdp, le_gdp$life_exp, xlab="GDP", ylab="Life Expectancy")
```

# Question 1E
```{r}
log_gdp <- log(le_gdp$gdp)
plot(log_gdp, le_gdp$life_exp, xlab="log(GDP)", ylab="Life Expectancy")
```
Yes, this looks like a linear relationship. 

# Question 1F
```{r}
m1 <- lm(le_gdp$life_exp ~ log_gdp)
summary(m1)
anova(m1)
```

# Question 1G
(Residual Standard Error)2 = 4.7832=22.877

# Question 1H
RSS = 22.877(163) = 3728.95
TSS = 7071.5 + 3728.7 = 10800.2 (used ANOVA table) 
R2= 1 - 3728.9510800.2= 0.6547564 
This appears under Multiple R-squared:  0.6548

# Question 1I
5.3860 years

# Question 2A
```{r}
data(teengamb)
mod1 <- lm(gamble ~ sex + status + income + verbal, data=teengamb)
summary(mod1)
```
Income and Sex are significant at the 0.05 level.

# Question 2B
22.12 pounds more than the female. 

# Question 2C
22.692(42) = 21623.12 = RSS













