---
title: "Homework 5"
output:
  pdf_document: default
  html_document: default
---

```{r, message = FALSE, warning = FALSE}
library(faraway)
library(ggplot2)
```

# Question 1A
```{r}
data(fortune)

ggplot(data=fortune) +
  geom_point(aes(x=age, y=wealth, shape=region))
```
The plot seems to show very little linear correlation between age on wealth. There are also a few very large outliers in the data. 

# Question 1B
```{r}


# Untransformed Model
lm_wealth <- lm(I(wealth^1) ~ age + region, data=fortune)
summary(lm_wealth)

plot(fitted(lm_wealth), residuals(lm_wealth), 
     main='Untransformed Residual Plot')
qqnorm(residuals(lm_wealth), main='Untransformed QQ Plot')
qqline(residuals(lm_wealth))

# Transformed Model
lm_wealth_transformed <- lm(I(wealth^-1) ~ age + region, data=fortune)
summary(lm_wealth_transformed)

plot(fitted(lm_wealth_transformed), residuals(lm_wealth_transformed), 
     main='Transformed Residual Plot')
qqnorm(residuals(lm_wealth_transformed), main='Transformed QQ Plot')
qqline(residuals(lm_wealth_transformed))
```

# Question 1C
y-1= 0.574005 - 0.001044xi1+ 0.075583xi2 +0.044024xi3 +0.051481xi4 +0.042186xi5 

xi1 - Age
xi2 - Europe
xi3 - Middle East
xi4 - Other
xi5 - USA
Reference Level: Asia

There doesn’t seem to be much of a relationship between age and region on wealth in this dataset. There are no predictors even close to being significant, and the adjusted R-squared is -0.009. 

# Question 2A
```{r}
data(pulp)
lm_pulp <- lm(bright ~ operator, data=pulp)
summary(lm_pulp)
anova(lm_pulp)
```
There appears to be a difference between the operators, as the operator p-value in the one-way ANOVA is significant at the 0.05 level (p value: 0.02261)

# Question 2B
```{r}
pairwise.t.test(pulp$bright, pulp$operator, p.adjust.method='none')
pairwise.t.test(pulp$bright, pulp$operator, p.adjust.method='bonferroni')
pairwise.t.test(pulp$bright, pulp$operator, p.adjust.method='fdr')
```
Pairwise t test without mht correction suggests the difference between level b and d is significant at the 0.01 level (p value: 0.0083. Pairwise t test with bonferroni correction suggest no factor levels are different at the 0.01 level. Same with fdr; however, the p values do get smaller and you see a difference between b and d as well as b and c at the 0.05 level. 

# Question 3A
```{r}
data(butterfat)

mature <- subset(butterfat, Age == 'Mature')
lm_butterfat <- lm(Butterfat ~ Breed, data=mature)
anova(lm_butterfat)
```
One-way Anova suggests there is a difference between the breeds as the p-value from the f test is highly significant (2e-16). 

# Question 3B
```{r}
plot(fitted(lm_butterfat), residuals(lm_butterfat), 
     main='Butterfat Residual Plot')
qqnorm(residuals(lm_butterfat), main='Butterfat QQ Plot')
qqline(residuals(lm_butterfat))
sum(hatvalues(lm_butterfat) > 2*5/50)
```
Variance might be a little higher as fitted value increases, but still seems to satisfy our assumptions. 
Residuals might be slightly long - tailed, but still seems to satisfy our assumptions. 
There are no large leverage values (no hat values greater than 2p/n). 

# Question 3C
```{r}
boxplot(Butterfat ~ Breed, data=mature)
pairwise.t.test(mature$Butterfat, mature$Breed, p.adjust.method='bonferroni')
```
All breeds are different from each other at the 0.05 level except Guernsey and Jersey as well as Ayrshire and Canada. This appears to be reflected in the boxplot. 

# Question 4
```{r}
data(prostate)

lm_prostate <- lm(lpsa ~ lcavol + lweight + age + lbph + svi + lcp + 
                    gleason + pgg45, data=prostate)

# Checking Leverage Points
sum(hatvalues(lm_prostate) > 2*9/97)
halfnorm(hatvalues(lm_prostate), main='Leverage Points', nlab=0)

# Checking Outliers 
rstud_pvals <- 2*pt(-abs(rstudent(lm_prostate)), 87)
sum(p.adjust(rstud_pvals, "bonferroni") < 0.05)
plot(fitted(lm_prostate), rstudent(lm_prostate), main='Studentized Residuals')

# Uncorrected Test of Outliers
sum(abs(rstudent(lm_prostate)) > 3)

# Checking Influential Points
sum(cooks.distance(lm_prostate) > 4/97)
halfnorm(cooks.distance(lm_prostate), main='Cooks Distance', nlab=0)
plot(lm_prostate, 5)
```
There are five points that could be potential leverage points.Looking at the leverage point plot, there looks to be one clear leverage point, and a few others could be, so five seems to make sense. 

Looking at the studentized residual plot , there are no residuals greater than three, so I don’t think there are any outliers. I also ran bonferri adjusted test for outliers and found zero. 

Looking at the cooks distance graph, there are atleast four points that I would say are influential (maybe as many as 7). Claude said the common heuristic for assessing influential points is checking cooks distance greater than 4/n. This resulted in seven points that could possibly be influential. 
